---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Anaelle Gackiere"
date: "03-06-2026"
output: github_document
---

## Load Packages and Data  

First, let's load the necessary packages:  

```{r load-packages, message = FALSE}
library(tidyverse) 
library(skimr)
```

Now, load the dataset. If your data isn't ready yet, you can leave `eval = FALSE` for now and update it when needed.  


```{r load-data, message = FALSE, eval = TRUE}
uoe_art <- read_csv("data/uoe-art.csv")
```

## Exercise 10

Let's start working with the **title** column by separating the title and the date:  

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, link)  
```


## Exercise 11  

*Write your answer here.*  

```{r skim}
skim(uoe_art)
```



## Exercise 12  

*Continue with the same structure as above.*

```{r simple-histogram}
ggplot(uoe_art, aes(x = year)) +
  geom_histogram(binwidth = 10)

```

```{r outlier-check}

uoe_art %>%
  filter(!is.na(year)) %>%
  arrange(year) %>%
  head(5)


```

# Exercise 13

```{r}

uoe_art <- uoe_art %>%
  mutate(year = if_else(year == 2, 1964, year))
ggplot(uoe_art, aes(x = year)) +
  geom_histogram(binwidth = 10)


```

# Exercise 14

```{r}

uoe_art %>%
  count(artist, sort = TRUE) %>%
  head()

```

The most commonly featured artist in the collection is **"Unknown"**. The university likely has many pieces of unknown artists because they might have been found or donated without any identifying information.


# Exercise 15

```{r}
childc <- uoe_art %>%
  filter(str_detect(title, regex("child", ignore_case = TRUE))) 
```

It appears that ```r nrow(childc)``` art pieces have the word “child” in their title.
